Aa Language Reference Manual

### 2023-12-26 v2/Ahir-asm/devel/docs/AaLRM.tex
Updated handling of records....   and checked out.

@@

Expressions in \Aa fall into the following classes
\begin{itemize}
\item Constant literal references.
\item Simple object references.
\item Indexed object references.
\item Pointer de-reference expressions.
\item Address-of expressions.
\item Unary expressions.
\item Useful Unary logical expressions.
\item Slice expressions.
\item Bitmap (bit permutation) expressions.
\item Binary expressions.
\item Ternary expressions.
\item Zero, One expressions.
\end{itemize}

@@

@@

\subsection{Opaque Modules}

>>>>

\subsection{The bit-level layout of a Record-type}

Consider a record type:
\begin{verbatim}
$record [myrec] <$uint<8> >  < $uint<16> >
\end{verbatim}
which has an 8-bit field and a 16-bit field.  The
record type when implemented in hardware will
use 24 bits organized as follows
\begin{verbatim}
[23:8]                [7:0]
second-field          first-field
   16bit                8bit
\end{verbatim}

A cast from the record type to an integer type
will be consistent with this bit layout.
For example
\begin{verbatim}
// concatenate fields last-field to first-field.
r := ($cast (myrec) ($concat u16 u8))

//
// The cast from the record gives the 
// last field as the left-most.
// w[23:8] will be field 2, 
// w[7:0]  will be field 1.
w := ($bitcast ($uint<24>) r) 
\end{verbatim}

Note that an assignment to an SSA variable
with record type which writes only to
a part of a record is not permitted.
That is
\begin{verbatim}
r [0] := ....
\end{verbatim}
is not permitted if $r$ is an SSA variable
with a record type.

@@

Expressions in \Aa fall into the following classes
\begin{itemize}
\item Constant literal references.
\item Simple object references.
\item Indexed object references.
\item Pointer de-reference expressions.
\item Address-of expressions.
\item Unary expressions.
\item Useful Unary logical expressions.
\item Slice expressions.
\item Bitmap (bit permutation) expressions.
\item Binary expressions.
\item Ternary expressions.
\item Zero, One expressions.
\item Funcion call expressions.
\end{itemize}

@@

\subsection{Function call expressions}

When a module is declared with only a single
output argument, then it can be ``called'' in
another way, using a function call expression.

For example
\begin{verbatim}
$module [add8] $in (X Y: $uint<8>) 
    $out(Z: $uint<8>)
$is
{
  Y := (X + 1)
}
\end{verbatim}

can be invoked in an expression as
\begin{verbatim}
P := ($call add8 (U V))
\end{verbatim}
for convenience.

@@

\subsection{Opaque Modules} \label{sec:Opaque}
